Merits of hypermedia systems

### 2013-06-07 dagstuhl-2013/position.tex
Use case
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@587 43ef1190-90fd-4dd7-a769-d0121f02b80e

>>>>

\section{Possible uses}

Over time, I believe that interfaces that require developers to read
external documentation will loose to interfaces where ``View Source''
is sufficient to learn everything that is needed. This is the essence
of hypermedia systems, in the RDF case, everything needed to program
is available in the RDF. It tells application what it may do next.

In the above, we have included mostly create, add and delete
primitives, but these could be refined for application scenarios if
needed.

For example a pizza baker publishes Linked Data about pizzas they
sell, including data sufficient to create a sophisticated search and
sales application. The Linked Data will then include triples that
state explicitly how the order should be placed, i.e. what resources
need updating. Moreover, the may not only want to sell pizzas, but
also drinks. Thus, the Linked Data presented to the application should
not only be a Symetric Concise Bounded Description, as common today,
but careful designed to provide exactly the data needed to optimize
sales.
